Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent

### 2014-10-21 manuscript/paper-tycho.tex
SN1006 damping fits, minor notes on ms text
Damped fit tables/plots, srcutlog, paper updates
Code for plots/tables showing damped/loss-limited fits
Add XSPEC local model srcutlog from Brian
Clean up old/unused tables
Generating script for Tycho tables with smaller ab, Bmin

\begin{abstract}
\note[Aaron]{Clone of AAS abstract}
Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
radiation at their forward shocks.  Thin rims have been taken to indicate that
shock-accelerated electrons rapidly cool downstream of the shock, requiring
strong magnetic field amplification.  But, magnetic field damping immediately
behind the shock could produce similarly thin rims.  Synchrotron loss-limited
rim widths should decrease with energy whereas damping limited rims should be
relatively energy-independent.  To discriminate between models, we measured rim
widths around Tycho's supernova remnant in 5 energy bands using an archival
$750 \unit{ks}$ \Chandra observation.  Rims narrow with increasing energy,
favoring loss-limited radiation over magnetic damping and corroborating similar
observations in the remnant of SN 1006. Observed widths are best fit by
electron transport models requiring amplified magnetic fields of
$\abt200$--$1000 \muG$ and particle diffusion coefficients $\abt
1$--$100\times$ Bohm values, consistent with prior work on Tycho's SNR.
Non-negligible diffusion results in some degeneracy between magnetic field
strength and diffusion coefficient in setting observed rim widths, but strong
magnetic fields are required for all measurements.  A different approach may be
needed to better constrain diffusion at supernova remnant shocks.
\end{abstract}

@@

% What are these shock rims, what is this acceleration?
Forward shock accelerated electrons in young supernova remnants (SNRs) emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream, producing a shell-like morphology with bright X-ray and radio
rims/filaments due to line-of-sight projection \citep{koyama1995}.  Although
synchrotron emission due to accelerated electrons does not imply acceleration
of an unseen hadronic component, the prevailing theory of diffusive shock
acceleration (DSA) should operate on both protons and electrons.  Observations
of these synchrotron rims, with other lines of direct and indirect evidence,
have built a case for hadron and lepton acceleration up to $\unit{PeV}$
energies in young supernova remnants \citep{uchiyama2007, aharonian2004,
acero2010, ackermann2013}.  Efficient hadron acceleration in supernova remnant
shocks is a prime candidate source for galactic cosmic rays up to the
cosmic ray spectrum's ``knee'' \citep{vink2012}.
\note[Aaron]{the discussion of hadronic acceleration isn't really relevant,
just background information}

@@

% What makes these shock rims?
The widths of these X-ray rims are controlled by a combination of
synchrotron losses, particle transport, and magnetic fields immediately
downstream of the shock.  Synchrotron losses depend on the initial electron
energy distribution and the gradual decrease of electron energies downstream of
the shock.  High energy electrons near the shock efficiently radiate harder
synchrotron X-ray photons, but decline in energy as they are transported away
from the shock; this may be seen in spectral softening downstream of the shock
\citep[e.g.,][]{cassam-chenai2007}.  The transport process is driven by bulk
plasma advection downstream of the shock and particle diffusion with respect to
bulk advection.  In general, diffusion allows higher energy electrons to
diffuse further upstream or downstream than would be expected from pure
advection.  Finally, the magnetic field strength may be quickly damped
downstream of the shock, so that electrons may not radiate as efficiently and
thin rims would reflect the spatial structure of the field, rather than
efficient particle acceleration (and losses) and/or efficient synchrotron
cooling \citep{pohl2005}.

% Whatever makes these shock rims also imposes energy dependence
Moreover, these controlling mechanisms predict different scalings for rim width
as a function of energy.  In the limiting case of constant magnetic field and
negligible particle diffusion, the rims are said to be synchrotron loss-limited
and rim widths should narrow with increasing photon frequency $\nu$ as
$\nu^{-1/2}$. Diffusion smears out rims at all energies with stronger effect at
higher energies, yielding a slower drop-off in rim widths when diffusion
dominates.  Magnetic damping, if at a length scale comparable to filament
widths, predicts comparatively energy-independent rim widths -- intuitively, if
the magnetic field turns off, synchrotron radiation turns off regardless of
electron energy.

@@

% Paper roadmap
Our procedure closely follows that of \citetalias{ressler2014}.
We first briefly review relevant transport models which fully account for
electron advection and diffusion with continuous synchrotron losses, as
considered by, e.g., \citet[and references therein]{berezhko2004} and
\citet{rettig2012}.  We selected and measured rim widths at several locations
around Tycho's forward shock, verifying that selected rims are free of thermal
line emission.  Using our model for particle transport (with DSA included, to
first order, in a simple exponentially cut-off injected electron spectrum), we
obtain estimates on magnetic field strength and diffusion coefficient
magnitude. We discuss the implications of our model fit results for
particle transport in Tycho, despite a significant degeneracy between
diffusion and synchrotron losses when diffusion is non-negligible.

@@

We consider two particle transport models that we fit to measurements of
Tycho's thin rim widths.  We measure the rim full widths at half maximum
(FWHMs) (Section~\ref{sec:fwhms}) and use the measurements to directly assess
width-energy dependence.  The measurements are also fit to the transport
models' predictions of rim FWHMs at multiple photon energies.  The models
accept three free parameters: magnetic field strength $B_0$, a scaled diffusion
coefficient $\eta_2$, and a diffusion-energy scaling exponent $\mu$.

@@

% TODO Choose names for these models and refer to them consistently, throughout
% TODO define ALL symbols, synchrotron constants, etc
\note[Aaron]{\citet{blandford1987} and other papers take a much more thorough
tack in deriving the relevant transport equations, drawing specifically from
plasma physics / DSA assumptions -- I suppose that much material is not
relevant or condensed into our diffusion coefficient $D$ (w/ stated Bohm
diffusion).  Is na\"ively citing generalized ``transport'' is sufficient here?
E.g., there is often a term of form $(E/3) (\del\cdot\vec{v}) (\ptl f/\ptl E)$,
neglected for steady downstream velocity (i.e., $\del\cdot\vec{v}=0$), which
would not arise out of our equations as stated.
See, e.g., equation (9) of \citet{skilling1975}.}
% Transport fundamentals
The energy and space distribution of electrons at a supernova remnant
controls the synchrotron rims we see in X-ray and radio.  We model electron
advection and diffusion from initial injection at the remnant's forward shock
assuming 1-D steady-state plane transport, with spatially homogeneous and
isotropic diffusion, as following the equation:
\begin{equation}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C .
\end{equation}
Here $f = f(E,x)$ is electron distribution as a function of electron energy $E$
and downstream distance $x$ (where the forward shock is at $x=0$ and $x>0$
towards the remnant's interior); $C$ is an arbitrary source/sink term, $D$ is
the diffusion coefficient, and $v_d$ is plasma velocity downstream of the
shock.  We consider only particle transport downstream of the shock ($x \geq
0$).  The source/sink term $C$ and diffusion coefficient $D$ conveniently
encapsulate all assumptions about the accelerated electron spectrum, shock
and magnetic field structure, and time/space evolution of the particle
distribution.  More sophisticated treatments may explicitly treat magnetic
fields and diffusion across the shock, plasma streaming instabilities and
particle losses, anisotropic diffusion, the DSA process and efficiency, and
other details in great depth \citep[e.g.,][and references therein]{reville2013,
bykov2014, ferrand2014}.

% Simple model
A first approximation is to let electrons have constant energy that is dumped
catastrophically after a synchrotron timescale $\tsynch = 1/(b B^2 E)$, where
$b = 1.57 \times 10^{-3}$ in CGS units and $B$ is magnetic field (which may
vary in space as $B=B(x)$).  The sink term is $C = -f / \tsynch$, yielding:
\begin{equation} \label{eq:simp-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
    \frac{f}{\tau_{\mt{synch}}} = 0 .
\end{equation}
No assumptions on the injected electron source term are necessary.
\citet{parizot2006} employed this model to derive estimates of magnetic fields,
diffusion coefficients, and electron spectrum cut-offs for several historical
SNRs.  Conveniently, equation~\eqref{eq:simp-mod} has analytic solution $f
\propto \exp(-x/a)$ where $a$ is a characteristic scale length.  The thin rim
FWHM predicted by equation~\eqref{eq:simp-mod} is:
\begin{equation} \label{eq:simp-fwhm}
    w = \frac{2\beta D / v_d}{\sqrt{1 +\frac{4D}{v_d^2 \tsynch}} - 1}
\end{equation}
with $\beta$ a projection factor relating $w$ to $a$ as $w = \beta a$
\citep{berezhko2004, parizot2006}.  We take $\beta = 4.6$ assuming a spatially
exponential $f(E,x)$ and projection from a spherical shell, as derived by
\citet{ballet2006}.

% Full model
A more accurate model accounts for continuous synchrotron losses as electrons
are injected from an exponentially cut-off power-law electron distribution
(normalization $K_0$, cut-off energy $\Ecut$) and transported downstream:
\begin{align} \label{eq:full-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =\;
    &K_0 E^{-s} e^{-E/\Ecut} \delta(x) \nonumber \\
    &+ \frac{\ptl}{\ptl E} \left(bB^2E^2f\right) ;
\end{align}
see \citet{webb1984}, \citet{berezhko2004}, \citet{cassam-chenai2007},
\citet{morlino2010}, \citet{rettig2012}, and references therein.
\citet{zirakashvili2007} have derived a different electron spectrum with a
steeper $\exp\left(- \left(E/\Ecut\right)^2\right)$ cut-off, but we follow
\citetalias{ressler2014} in using $E^{-s} e^{-E/\Ecut}$ for conceptual
simplicity.  The cut-off energy is determined by the diffusion coefficient $D$,
which we address in Section~\ref{sec:diffcoeff}.  To determine rim profiles and
widths, we first numerically solve for electron distribution $f(E,x)$ using
Green's function solutions by \citet{lerche1980} and \citet{rettig2012}; these
solutions are given by \citetalias{ressler2014} using notation similar to that
used herein \note[Aaron]{wording}.  The electron distribution may then be
integrated to obtain synchrotron emissivity:
\begin{equation} \label{eq:emissivity}
    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
\end{equation}
where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is one-particle synchrotron emissivity
with $K_{5/3}(z)$ a modified Bessel function of the second kind
\citep{pacholczyk1970}.  Integrating emissivity over lines of sight for a
spherical remnant yields intensity as a function of radial coordinate $r$:
\begin{equation} \label{eq:intensity}
    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
                    j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
\end{equation}
where $s$ is the line-of-sight coordinate.  A model FWHM may then be calculated
from the resulting intensity profile.

@@

% Define our diffusion coefficient, introduce fiducial energy
In our models, we consider a generalized diffusion coefficient with arbitrary
power-law dependence upon energy following, e.g., \citet{parizot2006}:
\begin{equation} \label{eq:diffcoeff}
    D(E) = \frac{\eta C_d E^\mu}{B}
         = \eta_h D_{\mt{B}}\left(E_h\right) \left(\frac{E}{E_h}\right)^\mu
\end{equation}
where $\mu$ parameterizes diffusion-energy scaling, and $\eta$ now has units
of $\mathrm{erg}^{1-\mu}$.
The right-hand side of equation~\eqref{eq:diffcoeff} introduces $\eta_h$, a
dimensionless diffusion coefficient scaled to the Bohm value at a fiducial
particle energy $E_h$.  This energy $E_h$ may be related to the emitted
synchrotron photons by taking the $\delta$-function approximation that an
electron of energy $E$ radiates at a singular frequency $\nu \propto E^2 B$ in
a magnetic field.  Note that $\eta_h$ and $\eta$ are related as
$\eta = \eta_h (E_h)^{1-\mu}$, and $\eta = \eta_h$ for Bohm-like diffusion
($\mu = 1$).

% Set choice of fiducial energy, eta_2
For subsequent analysis and model fitting, we take fiducial electron energy
$E_2 = E_h$ corresponding to a $2 \unit{keV}$ synchrotron photon and report all
model fit results in terms of $\eta_2 = \eta_h$.  Although the value of $E_2$
depends on magnetic field $B$ and may vary within the remnant, tying $\eta_h$
to a fixed observation energy gives a convenient and intuitive sense of
diffusion strength regardless of the underlying electron energies.
We also note that $\eta = \eta_2 (E_2)^{1-\mu}$.

@@

% Electron cut-off energy
With a diffusion coefficient in hand, we determine the electron spectrum
cut-off energy by equating synchrotron loss and diffusive acceleration
timescales.  For low energies and small synchrotron losses (cooling time longer
than acceleration time), electrons may be efficiently accelerated; near or
above the cut-off energy, electrons will radiate or escape too rapidly to be
accelerated, so the energy spectrum drops off steeply.  The cut-off energy
adapted from \citet{parizot2006} is given as:
\begin{align}
    \Ecut =
        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \muG}\right)^{-1/(1+\mu)} \nonumber \\
        &\times \left(\frac{v_s}{10^8 \unit{cm\;s^{-1}}}\right)^{2/(1+\mu)}
        \eta^{-1 / (1+\mu)} .
\end{align}
Note that this expression implicitly assumes (1) a strong shock with
compression ratio 4, and (2) isotropic magnetic turbulence both upstream and
downstream; see \citet{parizot2006} for a full derivation.

As the electron cut-off imposes a roll-off on SNR synchrotron flux,
estimates of the synchrotron roll-off frequency may provide an independent
observable to characterize shock conditions.
\note[Aaron]{todo: explore this?} % TODO FILL IN LATER -- NOT IMPORTANT NOW
\citet{miceli2013, yamazaki2014} looked at the synchrotron roll-off as a
diagnostic for electron spectrum cut-off behavior (whether loss or age limited)
and also infer various characteristics (particularly, $\eta > 1$ in SN 1006).
\citet{miceli2014-cloud} use azimuthal variation in synchrotron cut-off, with
other lines of evidence, to argue for the presence of a cloud interacting w/
the SW limb of SN 1006.

Speculation: could cloud interaction could be related to the sub-Bohm diffusion
observation in Sean's Filament 4?  The filament has many profiles, and looking
at Sean's data it looks like all the selections show a consistently strong drop
in FWHM.  \citet{miceli2013} argue that the concave distortion possibly
associated with the cloud is linked to a dip in synchrotron cut-off energies,
which they explain as being tied to a drop in shock velocity at the
indentation, due to the cloud.  If shock velocities are depressed, would more
diffusion / weaker B fields be necessary to explain the observed rim widths?
But we must still account for the quite strong width-energy drop-off!

\subsection{Magnetic damping}

% TODO REVISIT THIS AFTER SETTING UP CALCULATIONS
We also consider (not really) a magnetically damped field of form
\begin{equation}
    B(x) = B_{\mt{min}} + \left(B_0 + B_{\mt{min}}\right) \exp\left(-x / a_b\right) ,
\end{equation}
following \citet{pohl2005}.
In the full continuous energy loss model (equation~\eqref{eq:full-mod}), it
suffices to substitute $B = B(x)$ throughout; in the simpler model, $B(x)$
enters through the diffusion coefficient $D = D(E,x)$ and the analytic
expression (equation~\eqref{eq:simp-fwhm}) may no longer be valid.
Again, \citetalias{ressler2014} detail how to integrate a damped field into the
full model solutions.

(DRAFT) We currently do not present model fits with magnetic damping, although
in principle they are doable.  Set up the calculation w/ a range of scale
lengths (with $B_0$, $\eta_2$ chosen so that damping is the dominant control
for $0.7$--$7 \unit{keV}$), and compute FWHMs and $\mE$ values?

@@

% TODO REVISIT THIS AFTER SETTING UP CALCULATIONS
If magnetic damping is a primary control on rim widths, we expect to see $\mE
\sim -0.1$ \citepalias{ressler2014}.
\note[Aaron]{elaborate after filling in preceding section}

@@

% KEEP REGION NUMBER UPDATED
We selected 20 regions in 5 distinct filaments around Tycho's shock
(Figure~\ref{fig:snr}) based on the following criteria: (1) filaments should be
clear of spatial plumes of thermal ejecta in \Chandra images, which rules out,
e.g., areas of strong thermal emission on Tycho's eastern limb; (2) filaments
should be singular and localized; multiple filaments should either not
overlap or completely overlap (rules out parts of NE limb); (3) filament
peaks should be evident above the background signal or downstream thermal
emission (rules out faint southern filaments).  We accepted several
regions with poor quality peaks in the lowest energy band (0.7--1 keV) so long
as peaks in all higher energy bands were clear and well-fit.
\note[Aaron]{vague, imprecise}
We grouped regions into filaments by visual inspection of the remnant.
Within each filament, we chose region widths to obtain comparable counts
at the thin rim peak.
All measured rim widths are at least $1\arcsec$ and hence are resolved by
\textit{Chandra}'s point-spread function (PSF), which has FWHM of
$\abt 1\arcsec$ at $4\arcmin$ off-axis.

% TODO final figure should be higher quality, use vector overlay if possible
\begin{figure}
    \centering
    \plotone{figures/f0-snr-inv.png}
    \caption{RGB image of Tycho with region selections overlaid.  Image bands
    are 0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).  Bold region
    labels (1, 16) indicate region selections shown in
    Figures~\ref{fig:spec},~\ref{fig:profiles}.
    \note[Aaron]{Figure colors inverted to save ink.} \label{fig:snr}}
\end{figure}

@@

\begin{figure*}[ht]
    \plotone{figures/fig-profiles_01.pdf}
    \plotone{figures/fig-profiles_16.pdf}
    \caption{Best fit profiles with measured FWHMs demarcated for each energy
        band in Region 1 (top) and Region 16 (bottom).  Energy bands increase
        from left to right.  Data points in red were excluded from profile
        fitting domains as described in text.}
    \label{fig:profiles}
\end{figure*}

@@

For the rest of our results and discussion, we consider only full model
fit results in Tycho for simplicity.  We do reference the simple model to build
intuition and give scaling relations, as was done in depth by
\citet{parizot2006} and \citetalias{ressler2014}.

>>>>

\begin{abstract}
\note[Aaron]{Modified from AAS abstract - first pass update}
Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
radiation at their forward shocks.  Thin rims have been taken to indicate that
shock-accelerated electrons rapidly cool downstream of the shock, requiring
strong magnetic field amplification.  But, magnetic field damping immediately
behind the shock could produce similarly thin rims.  We measured rim widths
around Tycho's supernova remnant in 5 energy bands using an archival $750
\unit{ks}$ \Chandra observation.  Rims consistently narrow with increasing
energy and are well-described by either loss-limited or magnetically damped
models.  We are unable to distinguish between scenarios, as models for rim
widths incorporating electron cut-offs both reproduce the observed rim
drop-offs.  The best loss-limited fits require amplified magnetic fields of
$\abt200$--$1000 \muG$ and particle diffusion coefficients $\abt
1$--$100\times$ Bohm values, consistent with prior work on Tycho's SNR, whereas
magnetic damping fits permit magnetic fields of $\abt 10$--$300 \muG$ and
comparatively smaller diffusion coefficients (typically $\abt 1$--$10$).
Non-negligible diffusion coefficients, magnetic field strengths, and magnetic
damping lengthscales are somewhat degenerate in setting observed rim widths and
drop-offs.  A different approach will be needed to determine the presence of
magnetic damping downstream of supernova remnant shocks.
\end{abstract}

@@

% What are these shock rims, what is this acceleration?
Forward shock accelerated electrons in young supernova remnants (SNRs) emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream, producing a shell-like morphology with bright X-ray and radio
rims/filaments due to line-of-sight projection \citep{koyama1995}.  The
relatively strong synchrotron radiation, in conjunction with multiwavelength
spectra (radio, X-ray, gamma ray) \citep{aharonian2004, acero2010,
ackermann2013} and observations of rapid time variability \citep{uchiyama2007},
suggests that electrons are accelerated to PeV energies in young SNRs.
Although synchrotron emission due to accelerated electrons does not imply
acceleration of an unseen hadronic component, the prevailing theory of
diffusive shock acceleration (DSA) should operate on both protons and
electrons.  Efficient hadron acceleration in supernova remnant shocks is a
prime candidate source for galactic cosmic rays up to the cosmic ray spectrum's
``knee'' \citep{vink2012}.  \note[Aaron]{the discussion of hadronic
acceleration isn't really relevant, just background information}

@@

% What makes these shock rims?
The widths of these X-ray rims are controlled by a combination of
synchrotron losses, particle transport, and magnetic fields immediately
downstream of the shock.  Synchrotron losses depend on the initial electron
energy distribution and the gradual decrease of electron energies downstream of
the shock.  High energy electrons near the shock efficiently radiate harder
synchrotron X-ray photons, but decline in energy as they are transported away
from the shock; this may be seen in spectral softening downstream of the shock
\citep[e.g.,][]{cassam-chenai2007}.  The transport process is driven by bulk
plasma advection downstream of the shock and particle diffusion with respect to
bulk advection.  In general, diffusion allows higher energy electrons to
diffuse further upstream or downstream than would be expected from pure
advection.  Finally, the magnetic field strength may be quickly damped
downstream of the shock, so that electrons may not radiate as efficiently and
thin rims reflect the spatial structure of the field rather than efficient
particle acceleration (and losses) and/or efficient synchrotron cooling
\citep{pohl2005}.

% Whatever makes these shock rims also imposes energy dependence
Moreover, these controlling mechanisms predict different scalings for rim width
as a function of energy.  In the limiting case of constant magnetic field and
negligible particle diffusion, the rims are said to be synchrotron loss-limited
and rim widths should narrow with increasing photon frequency $\nu$ as
$\nu^{-1/2}$. Diffusion smears out rims at all energies with stronger effect at
higher energies, yielding a slower drop-off in rim widths when diffusion
dominates.  Magnetic damping, if at a length scale comparable to filament
widths, also favors more energy-insensitive rim widths -- intuitively, if the
magnetic field turns off, synchrotron radiation turns off regardless of
electron energy.

@@

% Paper roadmap
Our procedure closely follows that of \citetalias{ressler2014}.
We first introduce our transport models for electron advection and diffusion
with continuous synchrotron losses.  We selected and measured rim widths at
several locations around Tycho's forward shock, verifying that selected rims
are free of thermal line emission.  Using our models for particle transport
(with DSA included, to first order, in a simple exponentially cut-off injected
electron spectrum), we predict width-energy dependence in the loss-limited and
magnetic damping scenarios to obtain estimates on magnetic field strength and
diffusion coefficient magnitude.  We discuss degeneracy in our model fits and
the implications for future studies of young supernova remnant shocks.

@@

% Could just discuss one model...
We consider two particle transport models that we fit to measurements of
Tycho's thin rim widths.  We measure the rim full widths at half maximum
(FWHMs) (Section~\ref{sec:fwhms}) and compare our measurements to the transport
model predictions of rim FWHMs at multiple photon energies, for various input
parameters.  The models accept four free parameters: magnetic field strength
$B_0$, a scaled diffusion coefficient $\eta_2$, a diffusion-energy scaling
exponent $\mu$, and a magnetic damping lengthscale $a_b$ (an $e$-folding
length).

@@

% TODO Choose names for these models and refer to them consistently, throughout
% TODO define ALL symbols, synchrotron constants, etc
% Transport fundamentals
The energy and space distribution of electrons at a supernova remnant
controls the synchrotron rims we see in X-ray and radio.  We model electron
advection and diffusion from initial injection at the remnant's forward shock
assuming 1-D steady-state plane transport, with spatially homogeneous and
isotropic diffusion, as following the equation:
\begin{equation}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C .
\end{equation}
Here $f = f(E,x)$ is electron distribution as a function of electron energy $E$
and downstream distance $x$ (where the forward shock is at $x=0$ and $x>0$
towards the remnant's interior); $C$ is an arbitrary source/sink term, $D$ is
the diffusion coefficient, and $v_d$ is plasma velocity downstream of the
shock.  We consider only particle transport downstream of the shock ($x \geq
0$).  The source/sink term $C$ and diffusion coefficient $D$ conveniently
encapsulate all assumptions about the accelerated electron spectrum, shock
and magnetic field structure, and time/space evolution of the particle
distribution.  More sophisticated treatments may explicitly treat magnetic
fields and diffusion across the shock, plasma streaming instabilities and
particle losses, anisotropic diffusion, the DSA process and efficiency, and
other details in great depth \citep[e.g.,][and references therein]{reville2013,
bykov2014, ferrand2014}.

% Simple model
A first approximation is to let electrons have constant energy that is dumped
catastrophically after a synchrotron timescale $\tsynch = 1/(b B^2 E)$, where
$b = 1.57 \times 10^{-3}$ in CGS units and $B$ is magnetic field (which may
vary in space as $B=B(x)$).  The sink term is $C = -f / \tsynch$, yielding:
\begin{equation} \label{eq:simp-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
    \frac{f}{\tau_{\mt{synch}}} = 0 .
\end{equation}
No assumptions on the injected electron source term are necessary.
\citet{parizot2006} employed this model to estimate magnetic fields, diffusion
coefficients, and electron spectrum cut-offs for several historical SNRs.
Conveniently, equation~\eqref{eq:simp-mod} has analytic solution $f \propto
\exp(-x/a)$ where $a$ is a characteristic scale length.  The thin rim FWHM
predicted by equation~\eqref{eq:simp-mod} is:
\begin{equation} \label{eq:simp-fwhm}
    w = \frac{2\beta D / v_d}{\sqrt{1 +\frac{4D}{v_d^2 \tsynch}} - 1}
\end{equation}
with $\beta$ a projection factor relating $w$ to $a$ as $w = \beta a$
\citep{berezhko2004, parizot2006}.  We take $\beta = 4.6$ assuming a spatially
exponential $f(E,x)$ and projection from a spherical shell, as derived by
\citet{ballet2006}.

% Full model
A more accurate model accounts for continuous synchrotron losses as electrons
are injected from an exponentially cut-off power-law electron distribution
(normalization $K_0$, cut-off energy $\Ecut$) and transported downstream:
\begin{align} \label{eq:full-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =\;
    &K_0 E^{-s} e^{-E/\Ecut} \delta(x) \nonumber \\
    &+ \frac{\ptl}{\ptl E} \left(bB^2E^2f\right) ;
\end{align}
see \citet{webb1984}, \citet{berezhko2004}, \citet{cassam-chenai2007},
\citet{morlino2010}, \citet{rettig2012}, and references therein.
The cut-off energy is determined by the diffusion coefficient $D$,
which we address in Section~\ref{sec:diffcoeff}.  To determine rim profiles and
widths, we first numerically solve for electron distribution $f(E,x)$ using
Green's function solutions by \citet{lerche1980} and \citet{rettig2012}; these
solutions are given by \citetalias{ressler2014} using notation similar to that
used herein \note[Aaron]{wording}.  The electron distribution may then be
integrated to obtain synchrotron emissivity:
\begin{equation} \label{eq:emissivity}
    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
\end{equation}
where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is one-particle synchrotron emissivity
with $K_{5/3}(z)$ a modified Bessel function of the second kind
\citep{pacholczyk1970}.  Integrating emissivity over lines of sight for a
spherical remnant yields intensity as a function of radial coordinate $r$:
\begin{equation} \label{eq:intensity}
    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
                    j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
\end{equation}
where $s$ is the line-of-sight coordinate.  A model FWHM may then be calculated
from the resulting intensity profile.

@@

% Define our diffusion coefficient, introduce fiducial energy
In our models, we consider a generalized diffusion coefficient with arbitrary
power-law dependence upon energy following, e.g., \citet{parizot2006}:
\begin{equation} \label{eq:diffcoeff}
    D(E) = \frac{\eta C_d E^\mu}{B}
         = \eta_h D_{\mt{B}}\left(E_h\right) \left(\frac{E}{E_h}\right)^\mu
\end{equation}
where $\mu$ parameterizes diffusion-energy scaling, and $\eta$ now has units
of $\mathrm{erg}^{1-\mu}$.
The right-hand side of equation~\eqref{eq:diffcoeff} introduces $\eta_h$, a
dimensionless diffusion coefficient scaled to the Bohm value at a fiducial
particle energy $E_h$.  Note that $\eta_h$ and $\eta$ are related as
$\eta = \eta_h (E_h)^{1-\mu}$, and $\eta = \eta_h$ for Bohm-like diffusion
($\mu = 1$).

% Set choice of fiducial energy, eta_2
For subsequent analysis and model fitting, we take fiducial electron energy
$E_2 = E_h$ corresponding to a $2 \unit{keV}$ synchrotron photon and report all
model fit results in terms of $\eta_2 = \eta_h$.  Although the value of $E_2$
varies with magnetic field $B$ as $E_2 \propto B^{-1/2}$ and may vary within
the remnant, tying $\eta_h$ to a fixed observation energy gives a convenient
and intuitive sense of diffusion strength regardless of the underlying electron
energies.  We also note that $\eta = \eta_2 (E_2)^{1-\mu}$.

@@

% Electron cut-off energy
With a diffusion coefficient in hand, we determine the electron spectrum
cut-off energy by equating synchrotron loss and diffusive acceleration
timescales.  For low energies and small synchrotron losses (cooling time longer
than acceleration time), electrons may be efficiently accelerated; near or
above the cut-off energy, electrons will radiate or escape too rapidly to be
accelerated, so the energy spectrum drops off steeply.  The cut-off energy
adapted from \citet{parizot2006} is given as:
\begin{align} \label{eq:ecut}
    \Ecut =
        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \muG}\right)^{-1/(1+\mu)} \nonumber \\
        &\times \left(\frac{v_s}{10^8 \unit{cm\;s^{-1}}}\right)^{2/(1+\mu)}
        \eta^{-1 / (1+\mu)} .
\end{align}
\citet{parizot2006} derive equation~\eqref{eq:ecut} in the case $\mu=1$
assuming a strong shock with compression ratio 4 and isotropic magnetic
turbulence on both sides of the shock.

As the DSA imposed electron cut-off results in a roll-off on SNR synchrotron
flux, the synchrotron roll-off frequency may provide an independent observable
to estimate shock diffusion and is given by:
\begin{align} \label{eq:rolloff}
    \nu_{\mt{cut}} =
        &c_m \left(13.3 \unit{erg}\right)^{\frac{4}{1+\mu}}
        \left(0.2657 \unit{erg^2\;G}\right)^{-\frac{1-\mu}{1+\mu}} \nonumber \\
        &\left( 100 \muG \right)^{\frac{1-\mu}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \left( \eta_2 \right)^{-\frac{2}{1+\mu}} .
\end{align}
In particular, this equation is independent of magnetic field $B$ for all
values of $\mu$ (but recall that the specific electron energies associated with
$\eta_2$ will depend on $B$).

% Magnetic damping
\subsection{Magnetic damping}

We also consider a magnetically damped field of form
\begin{equation}
    B(x) = B_{\mt{min}} + \left(B_0 + B_{\mt{min}}\right) \exp\left(-x / a_b\right) ,
\end{equation}
following \citet{pohl2005}.
In the full continuous energy loss model (equation~\eqref{eq:full-mod}), it
suffices to substitute $B = B(x)$ throughout; in the simpler model, $B(x)$
enters through the diffusion coefficient $D = D(E,x)$ and the analytic
expression (equation~\eqref{eq:simp-fwhm}) may no longer be valid.
Again, \citetalias{ressler2014} detail how to integrate a damped field into the
full model solutions to equation~\eqref{eq:full-mod}.

%(DRAFT) We currently do not present model fits with magnetic damping, although
%in principle they are doable.  Set up the calculation w/ a range of scale
%lengths (with $B_0$, $\eta_2$ chosen so that damping is the dominant control
%for $0.7$--$7 \unit{keV}$), and compute FWHMs and $\mE$ values?

@@

% TODO REVISIT THIS AFTER SETTING UP CALCULATIONS
If magnetic damping is a primary control on rim widths, we expect to see $\mE
\sim -0.1$ \citepalias{ressler2014}.
\note[Aaron]{elaborate after filling in preceding section}
NOOOOOOOOOOOOOPE.

@@

% NOTE keep region/filament numbering up to date
We selected 20 regions in 5 distinct filaments around Tycho's shock
(Figure~\ref{fig:snr}) based on the following criteria: (1) filaments should be
clear of spatial plumes of thermal ejecta in \Chandra images, which rules out,
e.g., areas of strong thermal emission on Tycho's eastern limb; (2) filaments
should be singular and localized; multiple filaments should either not
overlap or completely overlap (rules out parts of NE limb); (3) filament
peaks should be evident above the background signal or downstream thermal
emission (rules out faint southern filaments).  We accepted several
regions with poor quality peaks in the lowest energy band (0.7--1 keV) so long
as peaks in all higher energy bands were clear and well-fit.
\note[Aaron]{vague, imprecise}
We grouped regions into filaments by visual inspection of the remnant.
Within each filament, we chose region widths to obtain comparable counts
at the thin rim peak.
All measured rim widths are at least $1\arcsec$ and hence are resolved by
\textit{Chandra}'s point-spread function (PSF), which has FWHM of
$\abt 1\arcsec$ at $4\arcmin$ off-axis.

% TODO final figure should be higher quality, use vector overlay if possible
\begin{figure}
    \centering
    \plotone{figures/f0-snr-inv.png}
    \caption{RGB image of Tycho with region selections overlaid.  Image bands
    are 0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).  Bold region
    labels (1, 16) indicate region selections shown in
    Figures~\ref{fig:spec},~\ref{fig:profiles}.  Filament 1: Regions 1--3,
    filament 2: regions 4--10, filament 3: regions 11-13, filament 4:
    regions 14--17, filament 5, regions 18--20.
    \label{fig:snr}}
\end{figure}

@@

\begin{figure*}%[ht]
    \plotone{figures/prfs_01.pdf}
    \plotone{figures/prfs_16.pdf}
    \caption{Best fit profiles with measured FWHMs demarcated for each energy
        band in Region 1 (top) and Region 14 (bottom).  Energy bands increase
        from left to right.  Data points in red were excluded from profile
        fitting domains as described in text.}
    \label{fig:profiles}
\end{figure*}

@@

\begin{figure*}[ht]
    \centering
    \plotone{figures/full-man_err-prfs_01.pdf}
    \plotone{figures/full-man_err-prfs_16.pdf}
    \caption{Full model rim profile width predictions for Regions 1
        (left) and 14 (right) with measured data.  Note that ordinate FWHM axes
        do not match and do not originate at zero, to better show model
        predictions and data variation.
    \label{fig:rims}}
\end{figure*}
